Merging Datasets Through Deep learning

### 2018-09-04 paper2018/datasets.tex
new figures
yehuda's edits

\subsection{Cleansing people's names}
Wikidata has a number of historical figures which are not really names of people (e.g. Queen Elizabeth, Pope Leo).  If we detected a title in the name referring to royalty or qualifiers or Roman numerals which strongly indicated royalty, we dropped the name.  We also removed punctuations such as '...', and anything that was placed in parenthesese because they were irrelevant to the name (e.g. a qualification such as the son of Jacob might appear in parentheses after a name).  Although we got the extract for English, there were frequently names in Chinese, Korean, Cyrillic, etc.  We removed these and restricted ourselves to names in ISO-8859-1 unicode.  All punctuations such as ',', '-', '.' etc were retained for names because they are strong indicators of how a name needs to be parsed.  People in wikidata have the main name for the entity, with aliases for the person specified in a different property.  We made sure that every alternate form had at least one name part in common with the main name to rule out 'nicknames' (e.g. `Father of the Nation' for George Washington).  We also dropped cases where the last name of a person was different (usually because a woman's name changed after marriage).

@@

\subsection{Augmenting people's names}
In many cases, we had no alternate forms for a person's name even if we did have their main name.  We augmented the data with the following rules.  If the main name for the person in Wikidata had two parts, we created new source forms as follows: (a) Last Name, First Name, (b) First Name Initial . Last Name, and (c) Last Name , First Name Initial.

If the main name in Wikidata had three parts, we created these additional source forms in addition to the ones listed above: (a) First Name Middle Name Initial Last Name (b) Last Name, First Name Middle Name (c) Last Name, First Name Middle Initial .

@@

\begin{figure*}[htb]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=.9\linewidth]{people_recall}
        \caption{Recall rate as a function of neighborhood size}
        \label{people_recall}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.5\textwidth}
        \centering 
        \includegraphics[width=.9\linewidth]{people_distances}
        \caption{Mean negative distance from anchor as a function of neighborhood size}
        \label{modified_loss}
    \end{subfigure}
    \label{people_distances}
    \caption{Characteristics of people data}
\label{people_characteristics}
\end{figure*}

\begin{figure*}[htb]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=.9\linewidth]{company_recall}
        \caption{Recall rate as a function of neighborhood size}
        \label{company_recall}
    \end{subfigure}%                                                                                                   
    ~
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=.9\linewidth]{company_distances}
        \caption{Mean negative distance from anchor as a function of neighborhood size}
        \label{modified_loss}
    \end{subfigure}
    \label{company_distances}
    \caption{Characteristics of company data}
\label{company_characteristics}
\end{figure*}

>>>>

\subsection{Cleansing people's names}
Wikidata has a number of historical figures which are not really names of people (e.g. Queen Elizabeth, Pope Leo).  If we detected a title in the name referring to royalty or qualifiers or Roman numerals which strongly indicated royalty, we dropped the name.  We also removed punctuations such as '...', and anything that was placed in parenthesese because they were not part of the name (e.g. a qualification such as the son of Jacob might appear in parentheses after a name).  Although we got the extract for English, there were frequently names in Chinese, Korean, Cyrillic, etc.  We removed these and restricted ourselves to names in ISO-8859-1 unicode.  All punctuations such as ',', '-', '.' etc were retained for names because they are strong indicators of how a name needs to be parsed.  People in wikidata have the main name for the entity, with aliases for the person specified in a different property.  We made sure that every alternate form had at least one name part in common with the main name to rule out 'nicknames' (e.g. `Father of the Nation' for George Washington).  We also dropped cases where the last name of a person was different (usually because a woman's name changed after marriage).

@@

\subsection{Augmenting people's names}
In many cases, we had no alternate forms for a person's name even if we did have their main name.  We augmented the data with the following rules.  If the main name for the person in Wikidata had two parts, we created new source forms as follows: (a) Last Name , First Name, (b) First Name Initial . Last Name, and (c) Last Name , First Name Initial.

If the main name in Wikidata had three parts, we created these additional source forms in addition to the ones listed above: (a) First Name Middle Name Initial Last Name (b) Last Name , First Name Middle Name (c) Last Name , First Name Middle Initial .

@@

\begin{figure}[htb]
    \centering
    \begin{subfigure}[t]{0.23\textwidth}
        \centering
        \includegraphics[width=.95\linewidth]{people_recall}
        \caption{Recall rate as a function of neighborhood size}
        \label{people_recall}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.23\textwidth}
        \centering 
        \includegraphics[width=.95\linewidth]{people_distances}
        \caption{Mean negative distance as a function of neighborhood size}
        \label{modified_loss}
    \end{subfigure}
    \label{people_distances}
    \caption{Characteristics of people data}
\label{people_characteristics}
\end{figure}

\begin{figure}[htb]
    \centering
    \begin{subfigure}[t]{0.23\textwidth}
        \centering
        \includegraphics[width=.99\linewidth]{company_recall}
        \caption{Recall rate as a function of neighborhood size}
        \label{company_recall}
    \end{subfigure}%                                                                                                   
    ~
    \begin{subfigure}[t]{0.23\textwidth}
        \centering
        \includegraphics[width=.99\linewidth]{company_distances}
        \caption{Mean negative distance from anchor as a function of neighborhood size}
        \label{modified_loss}
    \end{subfigure}
    \label{company_distances}
    \caption{Characteristics of company data}
\label{company_characteristics}
\end{figure}
